State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
Frequency analysis derivation

Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition. The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem. Thus, the minimum distance between basis must satisfy 
\begin{equation}
	\Delta_b < \frac{1}{2\nu_c}. 
\end{equation}
For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}. The Fourier transform of a Gaussian is another Gaussian with width $\sigma^2_{\nu}$ given by 
\begin{equation}
	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
\end{equation}
The relationship between the Fourier transform and the basis function width is 
\begin{equation}
	1234 
\end{equation}
Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.

>>>>

Similar considerations need to be made regarding the representation of the dynamic field $v_t(\mathbf{r})$ using the basis function decomposition. The minimum distance between adjacent basis functions also needs to satisfy Shannon's sampling theorem. Thus, the minimum distance between basis must satisfy 
\begin{equation}
	\Delta_b < \frac{1}{2\nu_c}. 
\end{equation}
For the Gaussian basis functions $\phi(\mathbf{r})$ being considered, the basis width parameter $\sigma_{\phi}^2$ can also be inferred from spectral considerations \cite{Sanner1992,Scerri2009}. The Fourier transform of an \textit{n}-dimensional Gaussian is another Gaussian given by
\begin{equation}\label{eq:GaussianFT}
\boldsymbol\Phi(\boldsymbol \nu)=\left(\frac{1}{\pi\sigma_{\nu}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left(-\frac{1}{\sigma_{\nu}^2}\boldsymbol\nu^\top \boldsymbol\nu\right).
\end{equation}
where 
\begin{equation}\label{eq:GaussianFTWidth}
	\sigma^2_{\nu} = \frac{1}{\pi^2\sigma_{\phi}^2}. 
\end{equation}
width $\sigma^2_{\nu}$ should be chosen to give at least 3 dB attenuation at $\boldsymbol\nu_c$ giving
\begin{equation}\label{eq:WidthFrequencyRelationship}
 \sigma^2_{\nu}=\frac{2\boldsymbol\nu_c^\top \boldsymbol\nu_c}{\ln 2}.
\end{equation}
This ensures that the basis functions can represent field with frequency content up to $\boldsymbol\nu_c $. Proof of \ref{eq:GaussianFT} and \ref{eq:WidthFrequencyRelationship} is given in Appendix
% Thus to ensure that the basis functions can represent fields with frequency content up to $\boldsymbol{\nu}_c$, $\sigma_{\nu}$ should be set with at least the 3~dB frequency for the basis functions equal to $\boldsymbol{\nu}_c$, thus obtained $\sigma^2_{\nu}$ and therefore $\sigma_{\phi}^2$.
